Considering scale in multilayer animal social networks

### 2020-06-16 paper/manuscript.Rmd
minor edits in discussion

Multilayer networks represent a novel framework for explicitly testing the
influence of habitat selection on sociality across scales. Animal social systems
can be parsed by spatial contexts, for example as defined by habitat types as in
Figure \@ref(fig:lcres). Given that habitat data are available across a wide
range of spatial scales, we evaluated the influence of habitat spatial
resolution on multilayer network metrics. The results indicate varied influence
of increasing spatial resolution depending on the habitat layer. As spatial
resolution increased, edge overlap decreased in forage while remaining stable in
open and forest habitats (Figure \@ref(fig:socres) D). Forage <!--Lichen? I think we need to call this lichen and not forage --> is a rare (<!--TODO--> XX % of the landscape) and
patchy habitat on Fogo Island, as is indicated by a decrease in the proportion
of relocations in this habitat type with increasing spatial resolution (Supplementary 1
Figure 1). Similar to increasing spatial distance threshold, the influence
of increasing spatial resolution on graph strength was notably different between
habitat layers. Forest layers showed little change in graph strength with
increasing spatial resolution and variation between individuals. Forage and open
layers had greater individual variation in graph strength, while forage was the
sole layer to show large responses in graph strength to increasing spatial
resolution (Figure \@ref(fig:socres) E). As such, multilayer network measures
related to habitat are explicitly dependent on spatial scale. Edge overlap can
indicate if some associations between individuals are dependent on the
habitat-context [@Battiston_2014]. If the spatial resolution of the habitat data
are insufficient to capture rare habitats, context-specific relationships
between individuals may not be captured by multilayer networks.

@@

The selection of time windows is essential for capturing sociality in specific
life stages of interest. Social phenotypes can change over ontogeny in ways that
can affect fitness [@Berger_2015; @Brent_2017]. Further complicating the issue,
individuals can vary in their rate of development [@Tarka_2018]. This variation
can make defining the appropriate temporal scale for testing the fitness
implications of an individual’s social phenotype over different stages of
ontogeny difficult. However, considering fine temporal scales has been show to
provide insight across developmental stages that may otherwise be missed
[@Turner_2017]. Furthermore, given the non-independent nature of social
interactions and associations, especially over time, it can be challenging to
test hypotheses about social dynamics with a suitable null control
[@Farine_2017; @Proskurnikov_2017]. Using the framework of multilayer networks,
ordinal layers of discrete time windows provide a way to make appropriate null
models to test questions about the dynamics of an individual’s social network
position over multiple aggregated time periods.

>>>>

Multilayer networks represent a novel framework for explicitly testing the
influence of habitat selection on sociality across scales. Animal social systems
can be parsed by spatial contexts, for example as defined by habitat types as in
Figure \@ref(fig:lcres). Given that habitat data are available across a wide
range of spatial scales, we evaluated the influence of habitat spatial
resolution on multilayer network metrics. The results indicate varied influence
of increasing spatial resolution depending on the habitat layer. As spatial
resolution increased, edge overlap decreased in forage while remaining stable in
open and forest habitats (Figure \@ref(fig:socres) D). Forage <!--Lichen? I think we need to call this lichen and not forage --> is a rare (<!--TODO--> XX % of the landscape) and
patchy habitat on Fogo Island, as is indicated by a decrease in the proportion
of relocations in this habitat type with increasing spatial resolution (Supplementary 1
Figure 1). Similar to increasing spatial distance threshold, the influence
of increasing spatial resolution on graph strength was notably different between
habitat layers. Forest layers showed little change in graph strength with
increasing spatial resolution and variation between individuals. Lichen and open
layers had greater individual variation in graph strength, while lichen was the
only layer to show large responses in graph strength to increasing spatial
resolution (Figure \@ref(fig:socres) E). As such, multilayer network measures
related to habitat are explicitly dependent on spatial scale. Edge overlap can
indicate if some associations between individuals are dependent on the
habitat-context [@Battiston_2014]. If the spatial resolution of the habitat data
are insufficient to capture rare habitats, context-specific relationships
between individuals may not be captured by multilayer networks.

@@

Selection of appropriate time windows is essential for capturing sociality in specific
life stages of interest. Social phenotypes can change over ontogeny in ways that
can affect fitness [@Berger_2015; @Brent_2017]. Further complicating the issue,
individuals can vary in their rate of development [@Tarka_2018]. This variation
can make defining the appropriate temporal scale for testing the fitness
implications of an individual’s social phenotype over different stages of
ontogeny difficult. However, considering fine temporal scales has been show to
provide insight across developmental stages that may otherwise be missed
[@Turner_2017]. Furthermore, given the non-independent nature of social
interactions and associations, especially over time, it can be challenging to
test hypotheses about social dynamics with a suitable null control
[@Farine_2017; @Proskurnikov_2017]. Using the framework of multilayer networks,
ordinal layers of discrete time windows provide a way to make appropriate null
models to test questions about the dynamics of an individual’s social network
position over multiple aggregated time periods.
